**The statistical analysis of non-linear longitudinal data in biomedical research using generalized additive models**

### 2021-03-05 Manuscripts/Manuscript_AM_v3.Rmd
Working on basis plot

plot(dat$y~dat$time)

matplot(dat$time, model_matrix[,-1], type = "l", lty = 2, add = T)
lines(y_pred ~ dat$time, col = "red", lwd = 2)

>>>>

time<-c(1:6)

basis1<-model_matrix[1:6,2]
basis2<-model_matrix[1:6,3]
basis3<-model_matrix[1:6,4]
basis4<-model_matrix[1:6,5]

plot(time,basis1,type='l')
plot(time,basis2,type='l')
plot(time,basis3,type='l')
plot(time,basis4,type='l')

#plot(dat$y~dat$time)

#matplot(dat$time, model_matrix[,-1], type = "l", lty = 2, add = T)

#lines(y_pred ~ dat$time, col = "red", lwd = 2)
